Technical Dimensions of Programming Systems

### 2022-01-26 prog-2022/prog22-master.tex
Rework Conceptualization -> Architecture and merge in FoC
Paper now 40pg long with <programming> class.

\documentclass[acmlarge, review=true
]{acmart}

\acmConference{}{2021}{}
\citestyle{acmauthoryear}

\markboth{}{}

@@

\author{Joel Jakubovic}
\affiliation{
\institution{University of Kent} \city{Canterbury} \country{UK}
}
\email{jdj9@kent.ac.uk}
\author{Jonathan Edwards}
\affiliation{}
\email{jonathanmedwards@gmail.com}
\author{Tomas Petricek}
\affiliation{
\institution{University of Kent} \city{Canterbury} \country{UK}
}
\email{T.Petricek@kent.ac.uk}

@@

\begin{document}

\maketitle
%\thispagestyle{empty}

\newcommand{\joel}[1]{}
\newcommand{\note}[1]{}
\newcommand{\tp}[1]{}
\providecommand{\tightlist}{}% Don't want Pandoc's tight lists
%\newcommand{\hypertarget}[1]{}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{prog22}
\end{document}

>>>>

\documentclass[english,submission]{programming}

%\citestyle{acmauthoryear}
%\markboth{}{}

% Class scrartcl Warning: seems someone has broken package `auxhook'.
% Usually this happens, if `auxhook' is loaded or used implicitly or explicitly
% by patching \document or via etoolbox command \AtEndPreamble. Trying an
% emergency workaround. You can avoid this warning adding:
\usepackage{auxhook}
% before \begin{document} on input line 6.
\begin{document}

\paperdetails{perspective=art, area=tbd}

@@

\author{Joel Jakubovic}
\affiliation{
University of Kent, Canterbury, UK
\email{jdj9@kent.ac.uk}
}
\author{Jonathan Edwards}
\affiliation{\email{jonathanmedwards@gmail.com}}
\author{Tomas Petricek}
\affiliation{
University of Kent, Canterbury, UK
\email{T.Petricek@kent.ac.uk}
}

\keywords{paper, lorem ipsum}

% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10003459</concept_id>
<concept_desc>General and reference~Computing standards, RFCs and guidelines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010476.10010477</concept_id>
<concept_desc>Applied computing~Publishing</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{General and reference~Computing standards, RFCs and guidelines}

\maketitle

@@

%\thispagestyle{empty}

\newcommand{\joel}[1]{}
\newcommand{\note}[1]{}
\newcommand{\tp}[1]{}
\newcommand{\mybox}[1]{\noindent\fbox{\parbox{\textwidth}{#1}}}
\providecommand{\tightlist}{}% Don't want Pandoc's tight lists
%\newcommand{\hypertarget}[1]{}

@@

\bibliography{prog22}
\end{document}
